Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-27 TACAS2018/paper.tex
sec 7

the plant precision $\mathbb{R}_{\langle P \rangle}$ and the controller's precision

@@

\paragraph{\underline{{\sc synthesize}}} generates a candidate controller $\mat{K}$
and observer $\mat{L}$ that satisfy

@@

which may choose to increase the plant's precision or return a synthesis failure.

@@

$\mathbb{R}_{\langle C \rangle}$ for the controller's representation

@@

\paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
system's abstraction as well as optimizes the current candidate
solution.
%
%% When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
%% where k is the iteration found for the counterexample.  
First, the system's abstraction must be refined in order to eliminate
the newly received counterexample. For this purpose,
we increase the time horizon $k$ for the
safety specification so that it captures the violating iteration
(for the given initial state) and adjust $\phi$:
$\phi = \phi \wedge \phi_{safety}^k$.
If the counterexample is provided by the {\sc continuous time} stage,
then we must select a smaller suitable sample time to be used
for the plant's discretization.
%% and modify the abstractions to meet the discretization 
%% ($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
%% It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
%\end{enumerate}

Secondly, we try to optimizes the failed candidate solution.
For this purpose, we seek to minimize the distance of the farthest point in the
reach space to the closest point to it in the safe region
\begin{equation}
e=max(\{min(\{\vec{x}-\vec{g} \mid \vec{g}\in G\}) \mid \vec{x} \in \hat{X}_\infty \}).
\label{eq:objective}
\end{equation}

Our optimization is iterative, following two stages.  The first stage
seeks to make the dynamics as convergent as possible, since convergent
dynamics are less likely to stray outside of the safe region (we say
less likely because the change in the eigenvectors changes the shape
of the space and may cause some trajectories to go further). For this
purpose, we take the largest eigenvalue and reduce it by a factor $f$
that still satisfies the controller constraints ($f \overline{\lambda}
\models \phi$).  The resulting observer and controller are then
verified against the safety specification $\phi_{safety}$ and the
objective $e$ is measured (Equation \eqref{eq:objective}).  If for
each iteration $k$, the objective $e_k<e_{k-1}$, we continue to
iterate until $e_k \leq 0$ (i.e. we found a safe controller),
otherwise we move to the second stage.

@@

 \end{tikzpicture}
}
\caption{CEGIS with Optimization Refinement. Orange boxes (light) are modelling
stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage.}
\label{fig:CEGIS-OR}
\end{figure}

@@

Our Synthesis Algorithm shows promise in exploiting modularity for
improved response. It however relies on the use of application
specific optimization which means that it is necessary to find adequate tools for
exploring different types of properties.  Our results show significant
improvement in terms of scalability over standard approaches with an ability to
explore complex properties, hence many synthesis tasks may be derived
from it. In particular we note that our synthesis loop should be targeted at
systems where the solution space is formed by connected spaces where
optimization algorithms or localized synthesis are likely to be achieved more
efficiently than global synthesis.
Finally our application to control synthesis provides a solid proof
of concept for scalable optimal control synthesis of LTI systems. There is still
a need to extend it it MIMO systems and analyse further properties, which may
also require exploring other optimization methods for control systems.

>>>>

the plant precision $\mathbb{R}_{\langle P \rangle}$ and the controller precision

@@

\paragraph{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}$
and observer matrix $\mat{L}$ that satisfy

@@

which may choose to increase the plant precision or return a synthesis failure.

@@

$\mathbb{R}_{\langle C \rangle}$ for the controller representation

@@

\paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
model abstraction as well as optimizes the current candidate
solution.
%
%% When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
%% where k is the iteration found for the counterexample.  
First, the model abstraction must be refined in order to eliminate
the newly received counterexample. For this purpose,
we increase the time horizon $k$ for the
safety specification so that it captures the violating iteration
(for the given initial state) and adjust $\phi$ as 
$\phi := \phi \wedge \phi_{safety}^k$.
If the counterexample is provided by the {\sc continuous time} stage,
then we must select a smaller suitable sample time to be used
for the model discretization.
%% and modify the abstractions to meet the discretization 
%% ($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
%% It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
%\end{enumerate}

Secondly, we try to optimizes the failed candidate solution.
For this purpose, we seek to minimize the distance of the farthest point in the
reach space to the closest point to it in the safe region
\begin{equation}
e = \max(\{\min(\{\vec{x}-\vec{g}, \vec{g}\in G\}), \vec{x} \in \hat{X}_\infty \}).
\label{eq:objective}
\end{equation}

Our optimization is iterative, following two stages.  The first stage
seeks to make the dynamics as convergent as possible, since convergent
dynamics are less likely to stray outside of the safe region (we say
less likely because the change in the eigenvectors changes the shape
of the space and may cause some trajectories to go further). For this
purpose, we take the largest eigenvalue and reduce it by a factor $f$
that still satisfies the controller constraints ($f \overline{\lambda}
\models \phi$).  The resulting observer and controller are then
verified against the safety specification $\phi_{safety}$ and the
objective $e$ is measured as in Equation \eqref{eq:objective}.   If for
each iteration $k$, the objective $e_k<e_{k-1}$, we continue to
iterate until $e_k \leq 0$ (i.e. we found a safe controller),
otherwise we move to the second stage.

@@

 \end{tikzpicture}
}
\caption{CEGIS-OR: CEGIS with Optimization Refinement. Orange boxes (light) are modelling
stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage.}
\label{fig:CEGIS-OR}
\end{figure}

@@

CEGIS-OR shows promise in exploiting modularity for improved response. 
It however relies on the use of application-specific optimization, 
which requires adequate tools for exploring different types of properties.  
Our results show significant improvement in terms of scalability over standard CEGIS approaches, 
with an ability to explore complex properties, hence many synthesis tasks may be tackled with it. 
In particular we note that our synthesis loop should be targeted at 
models where the solution space is formed by connected spaces where
optimization algorithms or localized synthesis are likely to be achieved more
efficiently than global synthesis \note{such solution spaces are unlikely classifiable a priori}. 
Finally our application to control synthesis provides a solid proof
of concept for scalable optimal control synthesis of LTI systems.

There is still a need to extend CEGIS-OR to MIMO models and to analyse more general properties, 
which may also require exploring other optimization methods for control systems.
